---
title: "View Reference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{View Reference}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

shinymvu uses [Alpine.js](https://alpinejs.dev/) for client-side reactivity.
You build your UI with standard `shiny::tags$` elements and pipe them through
`bind_*` and `on_*` helpers that add the necessary Alpine.js directives under
the hood.

This vignette is a reference for every binding and event helper. Each section
shows the shinymvu helper alongside the raw Alpine.js it produces, so you can
learn both at once.

All expressions reference `model`, the JavaScript object that holds your
current model state. The `send()` function dispatches messages to your R
`update` function.

# Displaying Text

`bind_text()` sets the text content of an element from a model field.

```{r}
tags$span() |>
  bind_text("model.count")
```

Raw Alpine.js equivalent:

```{r}
tags$span(`x-text` = "model.count")
```

Any element works:

```{r}
tags$h1() |>
  bind_text("model.title")

tags$p() |>
  bind_text("model.message")
```

If you need computed text like `"5 items"`, do the formatting in
`to_frontend` rather than writing JavaScript expressions:

```{r}
# In to_frontend:
to_frontend <- function(model) {
  list(
    count_label = paste0(
      length(model$items), " items"
    )
  )
}

# In the view:
tags$span() |>
  bind_text("model.count_label")
```

# Buttons

`on_click()` dispatches a message when the element is clicked.

```{r}
tags$button("+") |>
  on_click("increment")
```

Raw Alpine.js equivalent:

```{r}
tags$button(
  "+",
  `@click` = "send('increment')"
)
```

To send a static value with the message:

```{r}
tags$button("Page 2") |>
  on_click("set_page", 2)
```

# Text Input

`bind_value()` keeps an input in sync with the model. `on_input()` sends the
typed value as a message.

```{r}
tags$input(type = "text") |>
  bind_value("model.name") |>
  on_input("set_name")
```

Raw Alpine.js equivalent:

```{r}
tags$input(
  type = "text",
  `x-bind:value` = "model.name",
  `@change` = "send('set_name',
    $event.target.value)"
)
```

Use `debounce` to send on every keystroke (debounced) instead of on blur:

```{r}
tags$input(
  type = "text",
  placeholder = "Search..."
) |>
  bind_value("model.search") |>
  on_input("set_search", debounce = 300)
```

# Checkbox

`bind_checked()` syncs the checked state. `on_check()` sends the boolean
value.

```{r}
tags$input(type = "checkbox") |>
  bind_checked("model.agree") |>
  on_check("toggle_agree")
```

Raw Alpine.js equivalent:

```{r}
tags$input(
  type = "checkbox",
  `x-bind:checked` = "model.agree",
  `@change` = "send('toggle_agree',
    $event.target.checked)"
)
```

# Select Dropdown

```{r}
tags$select(
  tags$option(value = "red", "Red"),
  tags$option(value = "green", "Green"),
  tags$option(value = "blue", "Blue")
) |>
  bind_value("model.color") |>
  on_input("set_color")
```

Raw Alpine.js equivalent:

```{r}
tags$select(
  `x-bind:value` = "model.color",
  `@change` = "send('set_color',
    $event.target.value)",
  tags$option(value = "red", "Red"),
  tags$option(value = "green", "Green"),
  tags$option(value = "blue", "Blue")
)
```

# Number Input

`on_input_num()` coerces the value to a number before sending.

```{r}
tags$input(
  type = "number", min = "0", max = "120"
) |>
  bind_value("model.age") |>
  on_input_num("set_age")
```

Raw Alpine.js equivalent:

```{r}
tags$input(
  type = "number",
  `x-bind:value` = "model.age",
  `@change` = "send('set_age',
    Number($event.target.value))",
  min = "0",
  max = "120"
)
```

# Range / Slider

Same pattern as number input:

```{r}
tags$input(
  type = "range",
  min = "0", max = "100", step = "1"
) |>
  bind_value("model.volume") |>
  on_input_num("set_volume")
```

# Textarea

```{r}
tags$textarea(
  rows = "4",
  placeholder = "Tell us about yourself..."
) |>
  bind_value("model.bio") |>
  on_input("set_bio", debounce = 300)
```

# Password Input

```{r}
tags$input(type = "password") |>
  bind_value("model.password") |>
  on_input("set_password", debounce = 300)
```

# Date Input

```{r}
tags$input(type = "date") |>
  bind_value("model.birthday") |>
  on_input("set_birthday")
```

# Color Input

```{r}
tags$input(type = "color") |>
  bind_value("model.color") |>
  on_input("set_color")
```

# Radio Buttons

Each radio input sends the same message. `bind_checked()` takes a JavaScript
expression that compares the model value to the radio's value.

```{r}
tags$div(
  tags$input(
    type = "radio", name = "pet", value = "dog"
  ) |>
    bind_checked("model.pet === 'dog'") |>
    on_input("set_pet"),
  tags$label("Dog")
)

tags$div(
  tags$input(
    type = "radio", name = "pet", value = "cat"
  ) |>
    bind_checked("model.pet === 'cat'") |>
    on_input("set_pet"),
  tags$label("Cat")
)
```

Raw Alpine.js equivalent:

```{r}
tags$div(
  tags$input(
    type = "radio",
    name = "pet",
    value = "dog",
    `x-bind:checked` = "model.pet === 'dog'",
    `@change` = "send('set_pet',
      $event.target.value)"
  ),
  tags$label("Dog")
)
```

# Checkbox Group

For multi-select checkboxes, each dispatches the same message type with a
static value. Your `update` function toggles the value in/out of a list.

```{r}
tags$div(
  tags$input(
    type = "checkbox", value = "cheese"
  ) |>
    bind_checked(
      "model.toppings.includes('cheese')"
    ) |>
    on_change("toggle_topping", "cheese"),
  tags$label("Cheese")
)
```

Raw Alpine.js equivalent:

```{r}
tags$div(
  tags$input(
    type = "checkbox",
    value = "cheese",
    `x-bind:checked` =
      "model.toppings.includes('cheese')",
    `@change` = "send('toggle_topping', 'cheese')"
  ),
  tags$label("Cheese")
)
```

# File Input

`on_file()` extracts file metadata (name, size, type) and sends it as the
message value.

```{r}
tags$input(type = "file") |>
  on_file("upload")

tags$input(
  type = "file", multiple = NA, accept = "image/*"
) |>
  on_file("upload_photos")
```

# Key Events

`on_key()` dispatches a message when a specific key is pressed.

```{r}
tags$input(type = "text") |>
  bind_value("model.search") |>
  on_input("set_search", debounce = 300) |>
  on_key("enter", "submit_search") |>
  on_key("escape", "clear_search")
```

Raw Alpine.js equivalent:

```{r}
tags$input(
  type = "text",
  `x-bind:value` = "model.search",
  `@input.debounce.300ms` = "send('set_search',
    $event.target.value)",
  `@keydown.enter` = "send('submit_search')",
  `@keydown.escape` = "send('clear_search')"
)
```

# Conditional Show / Hide

`bind_show()` toggles an element's visibility with CSS `display`. The element
stays in the DOM.

```{r}
tags$div("Loading...") |>
  bind_show("model.loading")

tags$p(class = "text-danger") |>
  bind_show("model.error") |>
  bind_text("model.error")
```

You can combine `bind_show()` with other helpers:

```{r}
tags$button("Clear") |>
  bind_show("model.search.length > 0") |>
  on_click("clear")
```

# Conditional Render / Remove

`bind_if()` completely adds or removes an element from the DOM. Use it on a
`tags$template` wrapper.

```{r}
tags$template(
  tags$div("Welcome back!")
) |>
  bind_if("model.loggedIn")
```

Raw Alpine.js equivalent:

```{r}
tags$template(
  `x-if` = "model.loggedIn",
  tags$div("Welcome back!")
)
```

Use `bind_show()` for frequent toggles (cheaper, just CSS). Use `bind_if()`
when the element should not exist at all when the condition is false.

# List Rendering

`bind_for()` iterates over a list and renders each item. The first argument
is the loop variable name, the second is the model expression.

```{r}
tags$template(
  tags$li() |> bind_text("item")
) |>
  bind_for("item", "model.items")
```

Raw Alpine.js equivalent:

```{r}
tags$template(
  `x-for` = "item in model.items",
  tags$li(`x-text` = "item")
)
```

Use `bind_key()` for efficient DOM updates on keyed lists:

```{r}
tags$template(
  tags$li(
    tags$span() |> bind_text("item.text"),
    tags$button("X") |>
      on_click("delete", "item.id")
  ) |>
    bind_key("item.id")
) |>
  bind_for("item", "model.todos")
```

# Dynamic Attributes

`bind_disabled()` is a shorthand for the common disabled pattern:

```{r}
tags$button("Submit") |>
  bind_disabled("model.loading")
```

For any other attribute, use `bind_attr()`:

```{r}
tags$a() |>
  bind_attr("href", "model.url") |>
  bind_text("model.linkText")

tags$img() |>
  bind_attr("src", "model.avatarUrl") |>
  bind_attr("alt", "model.name")
```

# Dynamic CSS Class

`bind_class()` accepts a JavaScript expression. Use a ternary for
toggling a single class, or an object for multiple classes:

```{r}
tags$div() |>
  bind_class("model.isActive ? 'active' : ''")

tags$li() |>
  bind_class("{
    'completed': item.done,
    'editing': item.editing
  }")
```

# Dynamic Style

`bind_style()` accepts a JavaScript expression:

```{r}
tags$div(class = "progress-bar") |>
  bind_style(
    "'width: ' + model.progress + '%'"
  )

tags$div() |>
  bind_style("{
    opacity: model.visible ? 1 : 0.3
  }")
```

# Summary

**Event helpers** dispatch messages to your `update` function:

| Helper | Sends | Use with |
|---|---|---|
| `on_click(msg)` | No payload (or static value) | Buttons, any clickable |
| `on_input(msg)` | `$event.target.value` (string) | Text, select, date, color |
| `on_input_num(msg)` | `Number($event.target.value)` | Number, range |
| `on_check(msg)` | `$event.target.checked` (boolean) | Single checkbox |
| `on_change(msg, value)` | Static value | Checkbox group |
| `on_key(key, msg)` | No payload | Keyboard shortcuts |
| `on_file(msg)` | File metadata list | File input |

**Binding helpers** keep the DOM in sync with the model:

| Helper | Alpine.js directive |
|---|---|
| `bind_text(expr)` | `x-text` |
| `bind_value(expr)` | `x-bind:value` |
| `bind_checked(expr)` | `x-bind:checked` |
| `bind_show(expr)` | `x-show` |
| `bind_if(expr)` | `x-if` |
| `bind_for(var, expr)` | `x-for` |
| `bind_key(expr)` | `x-bind:key` |
| `bind_class(expr)` | `x-bind:class` |
| `bind_style(expr)` | `x-bind:style` |
| `bind_disabled(expr)` | `x-bind:disabled` |
| `bind_attr(name, expr)` | `x-bind:{name}` |
